{[}\href{todo.html}{Previous: Future Features \& Known Issues}{]}
{[}\href{index.html}{Contents}{]} {[}\href{contacts.html}{Next:
Contacts}{]}\\[2\baselineskip]

\section{Terrier Bibliography}\label{terrier-bibliography}

\subsection{Citing Terrier}\label{citing-terrier}

If you use Terrier during the course of your research, please cite:

\begin{itemize}
\tightlist
\item
  Craig Macdonald, Richard McCreadie, Rodrygo Santos and Iadh Ounis.
  From Puppy to Maturity: Experiences in Developing Terrier. In
  Proceedings of the SIGIR 2012 Workshop in Open Source Information
  Retrieval.
  {[}\href{http://terrierteam.dcs.gla.ac.uk/publications/macdonald12terrier.pdf}{PDF}{]}
  {[}\href{http://terrierteam.dcs.gla.ac.uk/publications/macdonald2012puppy.bib}{BibTex}{]}
  \textbf{(Preferred)}
\item
  Iadh Ounis, Christina Lioma, Craig Macdonald, and Vassilis Plachouras.
  Research Directions in Terrier: a Search Engine for Advanced Retrieval
  on the Web. In Novatica/UPGRADE Special Issue on Next Generation Web
  Search, 8(1):49--56, 2007.
  {[}\href{http://terrierteam.dcs.gla.ac.uk/publications/up8-1Ounis.pdf}{PDF}{]}
  {[}\href{http://terrier.org/publications/8380.bib}{BibTex}{]}
\item
  Iadh Ounis, Gianni Amati, Vassilis Plachouras, Ben He, Craig
  Macdonald, and Christina Lioma. Terrier: A High Performance and
  Scalable Information Retrieval Platform. In Proceedings of ACM
  SIGIR'06 Workshop on Open Source Information Retrieval (OSIR 2006).
  10th August, 2006. Seattle, Washington, USA.
  {[}\href{http://terrier.org/publications/ounis06terrier-osir.pdf}{PDF}{]}
  {[}\href{http://terrier.org/publications/ounis06terrier-osir.bib}{BibTeX}{]}
\item
  Iadh Ounis, Gianni Amati, Vassilis Plachouras, Ben He, Craig Macdonald
  and Douglas Johnson. Terrier Information Retrieval Platform. In
  Proceedings of the 27th European Conference on Information Retrieval
  (ECIR 05).
  {[}\href{http://terrier.org/publications/ounis05terrier.pdf}{PDF}{]}
  {[}\href{http://terrier.org/publications/ounis05terrier.bib}{BibTeX}{]}
\end{itemize}

\subsection{Package-specific
Citations}\label{package-specific-citations}

In addition, if you are developing upon one or more of the following
Terrier packages then please cite the associated paper as well:

\begin{itemize}
\tightlist
\item
  \href{javadoc/org/terrier/learning/package-summary.html}{org.terrier.learning}:
  Craig Macdonald, Rodrygo L.T. Santos, Iadh Ounis and Ben He. About
  Learning Models with Multiple Query Dependent Features. Transactions
  on Information Systems. 31(3):1-39. 2013.
  {[}\href{http://www.dcs.gla.ac.uk/~craigm/publications/macdonald13multquerydf.pdf}{PDF}{]}
  {[}\href{http://dl.acm.org/citation.cfm?id=2493176}{Bibtex}{]}
\item
  \href{javadoc/org/terrier/compression/package-summary.html}{org.terrier.compression}:
  Matteo Catena, Craig Macdonald, Iadh Ounis: On Inverted Index
  Compression for Search Engine Efficiency. In: Proc. ECIR '14 (2014)
  {[}\href{http://www.dcs.gla.ac.uk/~craigm/publications/catena14compression.pdf}{PDF}{]}
  {[}\href{http://link.springer.com/chapter/10.1007\%2F978-3-319-06028-6_30\#}{Bibtex}{]}
\end{itemize}

And link to the \href{http://terrier.org/}{Terrier Website} from your
homepage!

The
\href{http://terrierteam.dcs.gla.ac.uk/publications.html}{TerrierTeam
Publications} page has more references about the deployment of Terrier
in Information Retrieval research.

{[}\href{todo.html}{Previous: Future Features \& Known Issues}{]}
{[}\href{index.html}{Contents}{]} {[}\href{contacts.html}{Next:
Contacts}{]}

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

Webpage: \url{http://terrier.org}\\
Contact:
\href{mailto:terrier@dcs.gla.ac.uk}{\nolinkurl{terrier@dcs.gla.ac.uk}}\\
\href{http://www.dcs.gla.ac.uk/}{School of Computing Science}\\
Copyright (C) 2004-2015 \href{http://www.gla.ac.uk/}{University of
Glasgow}. All Rights Reserved.
