\section{\texorpdfstring{\href{}{}Documentation for Terrier
4.1}{Documentation for Terrier 4.1}}\label{documentation-for-terrier-4.1}

{[}\href{index.html}{Terrier Documentation}{]}
{[}\href{overview.html}{Next: Overview}{]}

\subsection{Introduction to Terrier}\label{introduction-to-terrier}

\href{overview.html}{Overview}

An overview of what the Terrier platform is, and what it can be used
for.

\href{whats_new.html}{What's New}

What has changed in the Terrier platform in the recent releases.

~

\subsection{Getting Started with
Terrier}\label{getting-started-with-terrier}

\href{quickstart.html}{Installing and Running Terrier}

Quickstart: Contains information about how to download, install and
start running Terrier, and an overview of the applications provided with
Terrier.

\href{basicComponents.html}{Terrier Components}

An overview of the main components of Terrier.

~

\subsection{Using Terrier}\label{using-terrier}

\href{configure_general.html}{Configuring Terrier}

A brief introduction to the configuration of Terrier

\href{configure_indexing.html}{Configuring Indexing}

A guide of indexing, and how it can be configured to your needs.

\href{configure_retrieval.html}{Configuring Retrieval}

A guide of the retrieval functionalities, covering frequently-used
retrieval methodologies, such as TF-IDF, Okapi's BM25, language models
(Hiemstra and Ponte \& Croft) and weighting models from the
probabilistic Divergence From Randomness (DFR), as well as query
expansion (pseudo-relevance feedback).

\href{learning.html}{Learning to Rank with Terrier}

A guide to using multiple retrieval features with learning to rank
techniques to enhance search effectiveness.

\href{querylanguage.html}{Terrier's Query Language}

A description of the query language that Terrier supports.

\href{evaluation.html}{Evaluation of Experiments}

Shows how the results of experiments can be evaluated using the in-built
evaluation package in Terrier.

\href{realtime_indices.html}{Real-time Index Structures}

An introduction to the real-time index structures in Terrier.

\href{terrier_desktop.html}{Desktop Search}

A guide to the included Desktop Search application of Terrier.

\href{terrier_http.html}{Web-based Terrier}

A guide to using the Web-based application of Terrier.

\href{website_search.html}{Website Search Application}

A guide to using the website search application, which illustrates
real-time crawling, indexing and retrieval functionalities in Terrier.

\href{trec_examples.html}{TREC Experiment Examples}

An example of how to create an index and produce a TREC run on the WT2G
and Blogs06 collections.

\href{hadoop_configuration.html}{Terrier/Hadoop Configuration}

A guide to how to configure Terrier to use a Hadoop cluster

\href{hadoop_indexing.html}{Hadoop MapReduce Indexing with Terrier}

A guide to using the Hadoop MapReduce indexer in Terrier.

\href{properties.html}{List of properties in Terrier}

Extensive list of properties that Terrier supports and what they
configure.

~

\subsection{Extending Terrier \& Other Advanced
Topics}\label{extending-terrier-other-advanced-topics}

\href{terrier_develop.html}{Developing with Terrier}

Introduction to developing applications using Terrier.

\href{extend_indexing.html}{Extending Indexing}

In depth guide about indexing, and the roles of each class in the
indexing process.

\href{extend_retrieval.html}{Extending Retrieval}

In depth guide about retrieval, and how various retrieval
functionalities can be integrated into Terrier, as well as, how you can
use Terrier to obtain various statistics about the terms and the
collection.

\href{compression.html}{Pluggable Compression}

A guide to configuring byte-level compression schemes to reduce the size
of Terrier's index structures.

\href{languages.html}{Non English language support}

Description of support functionalities in Terrier for indexing and
retrieving from documents written in languages other than English.

\href{dfr_description.html}{Description of DFR}

Description of the Divergence From Randomness framework that Terrier
implements.

\href{javadoc/index.html}{Terrier API Javadoc}

API documentation of each class in Terrier.

\href{todo.html}{Future Features \& Known Issues}

Upcoming features in future releases.

~

\subsection{Other Information}\label{other-information}

\href{http://terrier.org/forum/}{Terrier Forum}

The Terrier discussion forum is for developers and users of the Terrier
platform to discuss the software, ask questions, post patches and share
tips.

\href{http://ir.dcs.gla.ac.uk/wiki/Terrier}{Terrier Wiki}

Hints and tips, and configurations for various well-known corpora.

\href{bibliography.html}{Bibliography}

If you use Terrier in your research, please cite us!

\href{contacts.html}{Contacts}

Terrier Contacts

{[}\href{index.html}{Terrier Documentation}{]}
{[}\href{overview.html}{Next: Overview}{]}

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

Webpage: \url{http://terrier.org}\\
Contact:
\href{mailto:terrier@dcs.gla.ac.uk}{\nolinkurl{terrier@dcs.gla.ac.uk}}\\
\href{http://www.dcs.gla.ac.uk/}{School of Computing Science}\\
Copyright (C) 2004-2015 \href{http://www.gla.ac.uk/}{University of
Glasgow}. All Rights Reserved.

~
