{[}\href{index.html}{Contents}{]} {[}\href{whats_new.html}{Next: What's
new}{]}\\

\section{Terrier Features}\label{terrier-features}

Below, you can find a succinct list of features offered by Terrier.

\subsubsection{General}\label{general}

\begin{itemize}
\tightlist
\item
  Indexing support for common desktop file formats, and for commonly
  used TREC research collections (e.g. TREC CDs 1-5, WT2G, WT10G, GOV,
  GOV2, Blogs06, Blog08, ClueWeb09, ClueWeb12).
\item
  Many document weighting models, such as many parameter-free Divergence
  from Randomness weighting models, Okapi BM25 and language modelling.
\item
  \textbf{\emph{NEW!}} Supervised (machine learned) ranking models are
  supported via learning to rank.
\item
  Conventional query language supported, including phrases, and terms
  occurring in tags.
\item
  Handling full-text indexing of large-scale document collections, in a
  centralised architecture to at least 50 million documents, and using
  the Hadoop MapReduce distributed indexing scheme for even larger
  collections.
\item
  \emph{\textbf{NEW!}} Incremental indexing and retrieval capabilities
  to support real-time search
\item
  Modular and open indexing and querying APIs, to allow easy extension
  for your own applications and research.
\item
  Active Information Retrieval research fed into the Open Source
  platform.
\item
  Open Source (Mozilla Public Licence).
\item
  Written in cross-platform Java - works on Windows, Mac OS X, Linux and
  Unix.
\item
  Large user-base over 10 years of public release.
\end{itemize}

\subsubsection{Indexing}\label{indexing}

\begin{itemize}
\tightlist
\item
  Out-of-the box indexing of tagged document collections, such as the
  TREC test collections.
\item
  Out-of-the box indexing for documents of various formats, such as
  HTML, PDF, or Microsoft Word, Excel and PowerPoint files.
\item
  Out-of-the box support for distributed indexing in a Hadoop MapReduce
  setting.
\item
  Indexing of field information, such as the frequency of a term in a
  TITLE or H1 HTML tag.
\item
  Indexing of position information on a word, or a block (e.g. a window
  of terms within a distance) level.
\item
  Support for various encodings of documents (UTF), to facilitate
  multi-lingual retrieval.
\item
  Support for changing the tokenisation being used.
\item
  \emph{\textbf{NEW!}} Updatable indices to support real-time search
\item
  Indexing support for query-biased summarisation.
\item
  Support for fetching files to index by HTTP, allowing intranets to be
  easily searched.
\item
  \emph{\textbf{NEW!}} Highly compressed index disk data structures with
  built-in pluggable compression algorithms.
\item
  Highly compressed direct file for efficient query expansion.
\item
  Alternative faster single-pass and MapReduce based indexing.
\item
  Various stemming techniques supported, including the Snowball stemmer
  for European languages.
\end{itemize}

\subsubsection{Retrieval}\label{retrieval}

\begin{itemize}
\tightlist
\item
  Provides desktop, command-line and Web based querying interfaces.
\item
  Provides standard querying facilities, as well as Query Expansion
  (pseudo-relevance feedback).
\item
  Can be applied in interactive applications, such as the included
  \href{terrier_desktop.html}{Desktop Search}, or in a batch setting for
  research and experimentation.
\item
  Provides many standard document weighting models, including up to 126
  Divergence From Randomness (DFR) document ranking models, and other
  models such as Okapi BM25, language modelling and TF-IDF. Two new 2nd
  generation DFR weighting model, JsKLs and XSqrA\_M, are also included,
  which provide robust performance on a range of test collections
  without the need for any parameter tuning or training.
\item
  Advanced \href{querylanguage.html}{query language} that supports
  synonyms, +/- operators, phrase and proximity search, and fields.
\item
  \emph{\textbf{NEW!}} Learning-to-rank support enables out-of-the-box
  supervised ranking models.
\item
  Provides a number of parameter-free DFR term weighting models for
  automatic query expansion, in addition to Rocchio's query expansion.
\item
  Flexible processing of terms through a pipeline of components, such as
  stopword removers and stemmers.
\end{itemize}

\subsubsection{Experimentation}\label{experimentation}

\begin{itemize}
\tightlist
\item
  Handles all currently available TREC test collections - see
  \href{trec_examples.html}{TREC Experimentation Examples} for examples
  and known settings.
\item
  Easily scriptable to evaluate many parameter settings, or many
  weighting models in batch form.
\item
  Built-in \href{evaluation.html}{evaluation tools} for use with TREC
  ad-hoc and known-item search retrieval results, to produce various
  Precision and Recall measures.
\end{itemize}

{[}\href{index.html}{Contents}{]} {[}\href{whats_new.html}{Next: What's
new}{]}

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

Webpage: \url{http://terrier.org}\\
Contact:
\href{mailto:terrier@dcs.gla.ac.uk}{\nolinkurl{terrier@dcs.gla.ac.uk}}\\
\href{http://www.dcs.gla.ac.uk/}{School of Computing Science}\\
Copyright (C) 2004-2015 \href{http://www.gla.ac.uk/}{University of
Glasgow}. All Rights Reserved.
