{[}\href{dfr_description.html}{Previous: DFR Description}{]}
{[}\href{index.html}{Contents}{]} {[}\href{bibliography.html}{Next:
Bibliography}{]}\\

\section{Terrier Future Features and Known
Issues}\label{terrier-future-features-and-known-issues}

List of features and known issues that are marked for future Terrier
versions:\\

\subsection{Future Features}\label{future-features}

\begin{itemize}
\tightlist
\item
  Consider making Terrier available upon a Maven repository.
\item
  The addition of Terrier's own Exceptions for setup, indexing,
  querying.
\end{itemize}

\subsection{Known Issues}\label{known-issues}

\begin{itemize}
\tightlist
\item
  Building with Java 8 causes javadoc weirdness (compiles to wrong
  directory)
\item
  CompressionFactory/CompressionConfig is not supported by single-pass
  or Hadoop indexing.
\item
  Query language should be refined: In particular, ambiguity warnings
  when generating the parser with ANTLR should be removed, and a more
  structured query language should be introduced.
\item
  The real-time index structures do not currently support block indexing
\end{itemize}

\subsection{Deprecations, Scheduled
Refactorings}\label{deprecations-scheduled-refactorings}

The following classes and interfaces are/may be deprecated in this
version of Terrier and will likely be removed or refactored in a future
release:

\begin{itemize}
\tightlist
\item
  BlockLexiconEntry \& BlockFieldLexiconEntry will be removed in a
  future version of Terrier
\item
  \href{javadoc/org/terrier/utility/ApplicationSetup.html}{ApplicationSetup}
  will be replaced with a new non-global configuration API.
\item
  Terrier currently uses Hadoop version 0.20. Future releases of Terrier
  will upgrade to a later branch. Instructions to upgrade Terrier
  yourself can be found
  \href{http://ir.dcs.gla.ac.uk/wiki/Terrier/UpgradingHadoop}{here}
\end{itemize}

\textbf{Contributions}\\

All community contributions to the Terrier framework are welcome. In
addition, you can find more information about contributing on the
\href{http://terrier.org/}{Terrier website}.

{[}\href{dfr_description.html}{Previous: DFR Description}{]}
{[}\href{index.html}{Contents}{]} {[}\href{bibliography.html}{Next:
Bibliography}{]}

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

Webpage: \url{http://terrier.org}\\
Contact:
\href{mailto:terrier@dcs.gla.ac.uk}{\nolinkurl{terrier@dcs.gla.ac.uk}}\\
\href{http://www.dcs.gla.ac.uk/}{School of Computing Science}\\
Copyright (C) 2004-2015 \href{http://www.gla.ac.uk/}{University of
Glasgow}. All Rights Reserved.
